Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-03-14 paper/paper.tex
Funders

@@

\author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
Research Council [grant number EP/K503058/1]}\inst{1} \and Samba Ndojh Ndiaye\inst{2} \and Patrick
Prosser\inst{1} \and Christine Solnon \inst{3}}
\institute{University of Glasgow, Glasgow, Scotland \and
Universit\'e Lyon 1, LIRIS, UMR5205, F-69621, France  \and INSA-Lyon, LIRIS, UMR5205, F-69621, France}

>>>>

\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}

@@

\author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
    Research Council [grant number EP/K503058/1]}\inst{1} \and Samba Ndojh Ndiaye\thanks{This work
was supported by the ANR project SoLStiCe (ANR-13-BS02-0002-01)}\inst{2} \and Patrick
Prosser\inst{1} \and Christine Solnon\samethanks[2] \inst{3}}
\institute{University of Glasgow, Glasgow, Scotland \and
Universit\'e Lyon 1, LIRIS, UMR5205, F-69621, France  \and INSA-Lyon, LIRIS, UMR5205, F-69621, France}
